---
title: "ACORN AMR Report"
output: word_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flextable)
library(ggplot2)
library(grid)
library(gridExtra)
```

Report generated the `r Sys.time()`.

# Filters

This report is generated from the **filtered** patient and microbiology datasets in the ACORN App. You are enoucraged to generate as many reports as needed, using several different filters.

```{r eval = TRUE, echo=FALSE, results="asis"}
add_text <- function(text)  paste0(feedback_text, br(), text)
  
  # Summary
  start <- patient() %>% nrow()
  end <- patient_filter() %>% nrow()
  prop <- round(100 * end / start, 0)
  if(start == end) feedback_text <- paste0("All ", start, " patients selected")
  if(start != end) feedback_text <- paste0(end, " patients selected (", prop, "% of ", start, ")")
  
  # Surveillance Category
  if(input$filter_category == "CAI") feedback_text <- add_text("Community Acquired Infections")
  if(input$filter_category == "HAI") feedback_text <- add_text("Hospital Acquired Infections")
  
  # Type of ward
  if(! identical(input$filter_type_ward, sort(unique(patient()$ward)))) feedback_text <- add_text(paste0("Admitted in ", paste(input$filter_type_ward, collapse = ", "), " wards"))
  
  # Date of enrollment
  if(input$filter_enrollment[1] > min(patient()$date_enrollment) | input$filter_enrollment[2] < max(patient()$date_enrollment)) {
    feedback_text <- add_text(paste0("Enrolled between ", input$filter_enrollment[1], " and ", input$filter_enrollment[2]))
  }
  
  # Age
  if(input$filter_age_min > 0 | input$filter_age_max < 99) {
    feedback_text <- add_text(paste0("Aged ", input$filter_age_min, " to ", input$filter_age_max, " ", input$filter_age_unit))
  }
  if(! input$filter_age_na) {
    feedback_text <- add_text("Excluding missing ages")
  }
  
  # Patient diagnosis
  if(length(input$filter_diagnosis) != 3) {
    feedback_text <- add_text(paste0("Patients diagnosed with ", paste(input$filter_diagnosis, collapse = " or "), " only"))
  }
  
  # Diagnosis confirmation
  if(input$confirmed_diagnosis %in% c("Diagnosis confirmed", "Diagnosis rejected")) feedback_text <- add_text(paste0(input$confirmed_diagnosis, " by clinical outcome"))
  
  # Outcomes
  if(input$filter_outcome_clinical & !input$filter_outcome_d28)  feedback_text <- add_text("Patients with clinical outcome")
  if(!input$filter_outcome_clinical & input$filter_outcome_d28)  feedback_text <- add_text("Patients with D28-outcome")
  if(input$filter_outcome_clinical & input$filter_outcome_d28)  feedback_text <- add_text("Patients with clinical and D28-outcome")
  
  # Comorbidities
  if(input$filter_comorb)  feedback_text <- add_text("At least one Comorbidity")
  if(input$filter_cancer)  feedback_text <- add_text("With Cancer")
  if(input$filter_renal)  feedback_text <- add_text("With Chronic Renal Failure")
  if(input$filter_lung)  feedback_text <- add_text("With Chronic Lung Disease")
  if(input$filter_diabetes)  feedback_text <- add_text("With Diabetes mellitus")
  if(input$filter_malnutrition)  feedback_text <- add_text("With Malnutrition")
  
  # Clinical severity
  if(input$filter_clinical_severity)  feedback_text <- add_text("With one qSOFA/Paediatric severity point")
  
  # Prior hospitalisation
  if(input$filter_overnight_3months)  feedback_text <- add_text("With prior hospitalisation (in the past three months)")
  
  # Surgery
  if(input$filter_surgery_3months)  feedback_text <- add_text("With surgery in the past three months")
  
  # Presence of medical devices
  if(input$filter_medical_p_catheter)  feedback_text <- add_text("With Peripheral IV catheter")
  if(input$filter_medical_c_catheter)  feedback_text <- add_text("With Central IV catheter")
  if(input$filter_medical_u_catheter)  feedback_text <- add_text("With Urinary catheter")
  if(input$filter_medical_ventilation)  feedback_text <- add_text("With Intubation / Mechanical ventilation")
  
  # Ward
  if(! identical(input$filter_ward, sort(unique(patient()$ward_text))))  feedback_text <- add_text(paste0("Admitted in ", paste(input$filter_ward, collapse = ", "), " wards"))
  
  # Empiric Antibiotics Prescribed
  if(! is.null(input$filter_type_antibio)) feedback_text <- add_text(paste0("Prescribed with ", paste(input$filter_type_antibio, collapse = ", ")))
  
  # Return text
  return(HTML(feedback_text))
```


# Profile of Patients

## Total Number of Patients 

### Per Surveillance Category

Type of ward:

```{r}
patient_filter() %>%
  group_by(ward, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, ward) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
  
 
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(ward = "") %>%
  autofit()
```

</br>
Age Category:

```{r}
patient_filter() %>%
  mutate(age_category = case_when(
    age < 1 ~ "Less than 1",
    age < 5 ~ "1 to  5",
    TRUE ~ "Above 5")) %>%
  mutate(age_category = factor(age_category, levels = c("Less than 1", "1 to  5", "Above 5"))) %>% 
  group_by(age_category, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, age_category) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
  mutate(age_category = as.character(age_category)) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(age_category = "") %>%
  autofit()
```


</br>
Suspected Diagnosis:

```{r}
patient_filter() %>%
  group_by(surveillance_diag, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, surveillance_diag) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
 
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(surveillance_diag = "") %>%
  autofit()
```


</br>
Hospital Outcome:

```{r}
patient_filter() %>%
  mutate(clinical_outcome = as.character(clinical_outcome)) %>%
  mutate(clinical_outcome = recode(clinical_outcome, "TRUE" = "Hospital Outcome", "FALSE" = "No Hospital Outcome")) %>%
  group_by(clinical_outcome, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, clinical_outcome) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(clinical_outcome = "") %>%
  autofit()
```

</br>
Hospital Discharge Status:

```{r}
patient_filter() %>%
  group_by(discharge_status, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, discharge_status) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(discharge_status = replace_na(discharge_status, "Unknown")) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(discharge_status = "") %>%
  autofit()
```

</br>
Day 28 Outcome:

```{r}
patient_filter() %>%
  mutate(d28_outcome = as.character(d28_outcome)) %>%
  mutate(d28_outcome = recode(d28_outcome, "TRUE" = "Day 28 Outcome", "FALSE" = "No Day 28 Outcome")) %>%
  group_by(d28_outcome, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, d28_outcome) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(d28_outcome = "") %>%
  autofit()
```

</br>
Day 28 Status:

```{r}
patient_filter() %>%
  group_by(status_d28, surveillance_cat) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_cat, status_d28) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_cat, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(status_d28 = replace_na(status_d28, "Unknown")) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(status_d28 = "") %>%
  autofit()
```



### Per Diagnosis

Type of ward:

```{r}
patient_filter() %>%
  group_by(ward, surveillance_diag) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_diag, ward) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_diag, values_from = patients) %>%
  
 
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(ward = "") %>%
  autofit()
```

</br>
Age Category:

```{r}
patient_filter() %>%
  mutate(age_category = case_when(
    age < 1 ~ "Less than 1",
    age < 5 ~ "1 to  5",
    TRUE ~ "Above 5")) %>%
  mutate(age_category = factor(age_category, levels = c("Less than 1", "1 to  5", "Above 5"))) %>% 
  group_by(age_category, surveillance_diag) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_diag, age_category) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_diag, values_from = patients) %>%
  mutate(age_category = as.character(age_category)) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(age_category = "") %>%
  autofit()
```

</br>
Hospital Outcome:

```{r}
patient_filter() %>%
  mutate(clinical_outcome = as.character(clinical_outcome)) %>%
  mutate(clinical_outcome = recode(clinical_outcome, "TRUE" = "Hospital Outcome", "FALSE" = "No Hospital Outcome")) %>%
  group_by(clinical_outcome, surveillance_diag) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_diag, clinical_outcome) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_diag, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(clinical_outcome = "") %>%
  autofit()
```

</br>
Hospital Discharge Status:

```{r}
patient_filter() %>%
  group_by(discharge_status, surveillance_diag) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_diag, discharge_status) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_diag, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(discharge_status = replace_na(discharge_status, "Unknown")) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(discharge_status = "") %>%
  autofit()
```

</br>
Day 28 Outcome:

```{r}
patient_filter() %>%
  mutate(d28_outcome = as.character(d28_outcome)) %>%
  mutate(d28_outcome = recode(d28_outcome, "TRUE" = "Day 28 Outcome", "FALSE" = "No Day 28 Outcome")) %>%
  group_by(d28_outcome, surveillance_diag) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_diag, d28_outcome) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_diag, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(d28_outcome = "") %>%
  autofit()
```

</br>
Day 28 Status:

```{r}
patient_filter() %>%
  group_by(status_d28, surveillance_diag) %>%
  summarise(patients = n()) %>%
  ungroup() %>%
  complete(surveillance_diag, status_d28) %>%
  mutate(patients = replace_na(patients, 0)) %>%
  pivot_wider(names_from = surveillance_diag, values_from = patients) %>%
  
  # add totals
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total"))) %>%
  mutate(status_d28 = replace_na(status_d28, "Unknown")) %>%
  mutate(Total = rowSums(.[-1])) %>%
  
  # create table
  flextable() %>%
  set_header_labels(status_d28 = "") %>%
  autofit()
```

# Key Pathogens

Please note that "Susceptible" and "Intermediate" categories are here merged into one category labelled "Susceptible", following <a href = "http://www.eucast.org/newsiandr/" target = "_blank"> EUCAST new definitions of S, I and R from 2019.</a>


## Streptococcus pneumoniae


```{r}
# dev
# microbio_filter <- function() microbio
# corresp_org_antibio <- function() corresp_org_antibio
# organism_input <- "Acinetobacter baumannii"
# matching_name_column <- "a_baumannii"

organism_input <- "Streptococcus pneumoniae"
matching_name_column <- "s_pneumoniae"

nb <- microbio_filter() %>% filter(organism == organism_input) %>% nrow()

data <- microbio_filter() %>%
  filter(organism %in% organism_input) %>%
  select(specimen_id, 9:ncol(microbio_filter())) %>%
  pivot_longer(-specimen_id) %>%
  filter(value %in% c("S", "I", "R")) %>%
  mutate(value = recode(value, S = "Susceptible", I = "Susceptible", R = "Resistant")) %>%
  group_by(name) %>%
  count(value)

total_tested <- data %>%
  group_by(name) %>%
  summarise(total_org = sum(n))

sir_results <- data %>%
  left_join(total_tested, by = "name") %>%
  mutate(percent = round(100*n / total_org, 1))

sir_results <- left_join(sir_results, corresp_org_antibio(), by = c('name' = 'antibio_code')) %>%
  filter(UQ(as.symbol(matching_name_column)) == "show")


cols_sir <- c("#2166ac", "#b2182b")  # resp. S, R

print(sir_results)

g1 <- ggplot(sir_results, aes(x = antibio_name, y = percent, fill = value)) +
  geom_bar(stat = "identity", color = "gray10") +
  labs(x = NULL, y = "Antibio", fill = "Status") +
  scale_fill_manual(values = cols_sir) +
  theme_minimal(base_size = 16) +
  theme(panel.spacing = unit(2, "lines"), panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle = 30, hjust = 0.5, vjust = 1),
        legend.position = "top") +
  scale_x_discrete()

g2 <- ggplot(sir_results, aes(x = antibio_name, y = percent, fill = value)) +
  geom_bar(stat = "identity", color = "gray10") +
  labs(x = NULL, y = "Antibio", fill = "Status") +
  scale_fill_manual(values = cols_sir) +
  theme_minimal(base_size = 16) +
  theme(panel.spacing = unit(2, "lines"), panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle = 30, hjust = 0.5, vjust = 1),
        legend.position = "top") +
  scale_x_discrete()

g3 <- ggplot(sir_results, aes(x = antibio_name, y = percent, fill = value)) +
  geom_bar(stat = "identity", color = "gray10") +
  labs(x = NULL, y = "Antibio", fill = "Status") +
  scale_fill_manual(values = cols_sir) +
  theme_minimal(base_size = 16) +
  theme(panel.spacing = unit(2, "lines"), panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle = 30, hjust = 0.5, vjust = 1),
        legend.position = "top") +
  scale_x_discrete()


# t <- textGrob(paste0(organism_input, br(),
#                      microbio_filter() %>% filter(organism == organism_input) %>% nrow()))

t <- textGrob("Hello World")
grid.arrange(t, g1, g2, g3, ncol = 2)
# g1
```

- Overall Susceptibility Graph (All Infections)
- Susceptibility Graph for HAI
- Susceptibility Graph for CAI

